R Notebook

### 2016-10-03 manuscript/draft.Rmd
some SDM stuff

Quality of predictions is important:
  * helps determine policy/set priorities
  * something something climate change
  * need to know both accuracy of point estimates and how reasonable our prediction intervals are.
  * Overconfident predictions can be worse than uncertainty
  * Quality of prediction is one metric for how much we know about ecological processes
Dominant method is stacked SDMs:
  *
Difficult to test model assumptions/predictions because of time scales
  * Most scientists making predictions today will have retired by 2050
  * Use long-term data sets such as BBS to evaluate predictive skill
    * Note the large change in average temperatures since the 80's; comparable to the changes expected in the next N years
  * Test with simple baselines (e.g. random walk, future-is-like-present)
  * Focus on richness/diversity because \[citations saying that it's important\]

>>>>

Quality of predictions is important:
  * helps determine policy/set priorities
  * something something climate change
  * need to know both accuracy of point estimates and how reasonable our prediction intervals are.
  * Overconfident predictions can be worse than uncertainty
  * Quality of prediction is one metric for how much we know about ecological processes
Dominant method is stacked SDMs:
  * Strong assumptions (see "misc" below), many *interesting* predictions
  * Potential problems with confidence intervals
  * Potential disconnect between training target and actual goals
Difficult to test model assumptions/predictions because of time scales
  * Most scientists making predictions today will have retired by 2050
  * Use long-term data sets such as BBS to evaluate predictive skill
    * Note the large change in average temperatures since the 80's; comparable to the changes expected in the next N years
  * Test with simple baselines (e.g. random walk, future-is-like-present)
  * Focus on richness/diversity because \[citations saying that it's important\]
